TBD

### 2021-03-07 outputs/paper/paper.Rmd
update

set.seed(123)
FS_tree<-randomForest(post_favor_Sanders~., data=FS, ntree=500)
FS_importance <- importance(FS_tree)
FS_varImportance <- data.frame(Variables = row.names(FS_importance), 
                            Importance = FS_importance[ ,'MeanDecreaseGini'])
FS_varImportance <- as.data.frame(FS_varImportance)
max(FS_varImportance$Importance)
FS_varImportance_sort <- arrange(FS_varImportance,desc(Importance))

>>>>

set.seed(123)
FS_tree<-randomForest(post_favor_Sanders~., data=FS, importance=TRUE,proximity=TRUE)

FS_tree<-as.data.frame(FS_tree$importanceSD)
plot(FS_tree$`FS_tree$importanceSD`,top=20)

FS_importance <- importance(FS_tree)

library(caret)
FS_varImportance <- varImp(FS_tree,scale = FALSE)

plot(FS_varImportance, top = 20)

FS_varImportance <- data.frame(Variables = row.names(FS_importance), 
                            Importance = FS_importance[ ,'MeanDecreaseGini'])
FS_varImportance <- as.data.frame(FS_varImportance)
max(FS_varImportance$Importance)
FS_varImportance_sort <- arrange(FS_varImportance,desc(Importance))
